### 2023-12-01 manuscript.tex
Updated enrichment analysis method with multiple testing procedure
Added new enrichment table to main text

\subsection{GO term analyses}
The 2022-03-22 go-basic release of the Gene Ontology was obtained from the GO Consortium website~\cite{Ashburner2000, 2020GOConsortium}. The gene association file for the 2022\_02 release of the \textit{D. melanogaster} genome annotation was obtained from FlyBase~\cite{Gramates2022}. Obsolete annotations were dropped, and the remaining annotations were filtered by qualifiers and evidence code. The allowed qualifiers were ``enables,'' ``contributes\_to,'' ``involved\_in,'' ``located\_in,'' ``part\_of,'' and ``is\_active\_in.'' The allowed evidence codes were all experimental sources, traceable author statement (TAS), and inferred by curator (IC). The annotations were propagated up the ontology graph and joined with the region sets, so every annotation associated with a gene was associated with the regions derived from that gene. \textit{P}-values were calculated with exact hypergeometric probabilities with regions considered as the sampling unit. For the disorder score analysis, the reference set was the filtered regions, and the enrichment set was the regions in the upper decile of the score rate distribution (Fig.~\ref{sfig:scores_histogram}). For the cluster analysis, the reference set was the regions after the additional filtering by substitution rates, and the enrichment sets were the regions in each cluster.

@@

\clearpage
\section*{Figures}

@@

>>>>

\subsection{GO term analyses}
The 2022-03-22 go-basic release of the Gene Ontology was obtained from the GO Consortium website~\cite{Ashburner2000, 2020GOConsortium}. The gene association file for the 2022\_02 release of the \textit{D. melanogaster} genome annotation was obtained from FlyBase~\cite{Gramates2022}. Obsolete annotations were dropped, and the remaining annotations were filtered by qualifiers and evidence code. The allowed qualifiers were ``enables,'' ``contributes\_to,'' ``involved\_in,'' ``located\_in,'' ``part\_of,'' and ``is\_active\_in.'' The allowed evidence codes were all experimental sources, traceable author statement (TAS), and inferred by curator (IC). The annotations were propagated up the ontology graph and joined with the region sets, so every annotation associated with a gene was associated with the regions derived from that gene. \textit{P}-values were calculated with exact hypergeometric probabilities with regions considered as the sampling unit. For the disorder score analysis, the reference set was the filtered regions, and the enrichment set was the regions in the upper decile of the score rate distribution (Fig.~\ref{sfig:scores_histogram}). For the cluster analysis, the reference set was the regions after the additional filtering by substitution rates, and the enrichment sets were the regions in each cluster. Additionally, in the cluster analysis, tests were only performed for terms associated with at least two regions, and the set of $p$-values for each cluster were corrected for multiple testing using the Benjamini-Hochberg method.

@@

\clearpage
\section*{Figures and tables}

@@

\begin{landscape}
\begin{table}[h!]
\caption{\textbf{Significantly enriched terms in clusters.}}
\label{table:cluster_terms}
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
\textbf{Cluster} & \textbf{\begin{tabular}[c]{@{}l@{}}Regions\\ in cluster\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Regions\\ with term\end{tabular}} & \textbf{p-value} & \textbf{\begin{tabular}[c]{@{}l@{}}Corrected\\ p-value\end{tabular}} & \textbf{Term ID} & \textbf{Term name}                                                                                      \\ \hline
4                & 158                                                                   & 3                                                                    & 3.36E-05         & 9.93E-03                                                             & GO:0001671       & ATPase activator activity                                                                               \\ \hline
4                & 158                                                                   & 3                                                                    & 3.36E-05         & 9.93E-03                                                             & GO:0140677       & molecular function activator activity                                                                   \\ \hline
4                & 158                                                                   & 7                                                                    & 2.46E-04         & 4.84E-02                                                             & GO:0044281       & small molecule metabolic process                                                                        \\ \hline
6                & 44                                                                    & 2                                                                    & 1.58E-04         & 4.42E-02                                                             & GO:0044319       & wound healing, spreading of cells                                                                       \\ \hline
12               & 146                                                                   & 15                                                                   & 3.05E-05         & 1.65E-02                                                             & GO:0008104       & protein localization                                                                                    \\ \hline
12               & 146                                                                   & 16                                                                   & 6.42E-05         & 1.74E-02                                                             & GO:0033036       & macromolecule localization                                                                              \\ \hline
12               & 146                                                                   & 8                                                                    & 1.51E-04         & 2.73E-02                                                             & GO:0045184       & establishment of protein localization                                                                   \\ \hline
12               & 146                                                                   & 6                                                                    & 5.38E-04         & 4.88E-02                                                             & GO:0008233       & peptidase activity                                                                                      \\ \hline
12               & 146                                                                   & 7                                                                    & 5.03E-04         & 4.88E-02                                                             & GO:0015031       & protein transport                                                                                       \\ \hline
12               & 146                                                                   & 5                                                                    & 5.73E-04         & 4.88E-02                                                             & GO:0035592       & \begin{tabular}[c]{@{}l@{}}establishment of protein localization\\ to extracellular region\end{tabular} \\ \hline
12               & 146                                                                   & 5                                                                    & 6.31E-04         & 4.88E-02                                                             & GO:0071692       & protein localization to extracellular region                                                            \\ \hline
26               & 141                                                                   & 2                                                                    & 1.66E-04         & 3.42E-02                                                             & GO:0031543       & peptidyl-proline dioxygenase activity                                                                   \\ \hline
26               & 141                                                                   & 2                                                                    & 1.66E-04         & 3.42E-02                                                             & GO:0019511       & peptidyl-proline hydroxylation                                                                          \\ \hline
26               & 141                                                                   & 2                                                                    & 1.66E-04         & 3.42E-02                                                             & GO:0018126       & protein hydroxylation                                                                                   \\ \hline
38               & 82                                                                    & 4                                                                    & 8.30E-05         & 3.78E-02                                                             & GO:0010369       & chromocenter                                                                                            \\ \hline
\end{tabular}
\end{table}
\end{landscape}
